simon_test_loop

### 2019-03-20 src/stack_test.Rmd
some maxentvariableselection playing, and update to potential change to background point extraction

```{r}
janaball <- read.csv("../output/bio/background_10k.csv", header = TRUE)
janpresall <- read.csv("../output/bio/pres_nomissing.csv", header = TRUE)
janpresaball <- rbind.fill(janaball, janpresall)
janpresaball <- subset(janpresaball, month == 1)
janpresaball <- subset(janpresaball, select = c(occurrence, longitude_meters, latitude_meters, temp_depth, temp_surface, chl_depth, chl_surface, o2_depth, o2_surface, salinity_depth, salinity_surface, ssh_surface, mlp_surface, nao_sample, nao_prev, nao_winter, amo_sample, amo_prev, amo_winter))
names(janpresaball)[names(janpresaball)=="occurrence"] <- "species"
names(janpresaball)[names(janpresaball)=="longitude_meters"] <- "longitude"
names(janpresaball)[names(janpresaball)=="latitude_meters"] <- "latitude"
janpresall <- subset(janpresaball, species == 1)
janpresall$species <- replace(janpresall$species, janpresall$species == "1", "fish")
write.csv(janpresall, "../output/maxentvariableselection/presence.csv", row.names = FALSE)
janaball <- subset(janpresaball, species == 0)
janpresall$species <- replace(janpresall$species, janpresall$species == "0", "bg")
write.csv(janaball, "../output/maxentvariableselection/background.csv", row.names = FALSE)

VariableSelection(maxent="C:/Users/bunny/Downloads/maxent/maxent.jar", outdir=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/output"), gridfolder=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/testgrid"), occurrencelocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/presence.csv"), backgroundlocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/background.csv"), additionalargs="nolinear noquadratic noproduct nothreshold noautofeature", contributionthreshold=5, correlationthreshold=0.9, betamultiplier=seq(0.5, 4, 0.25))
```

>>>>

with all variables
```{r}
janaball <- read.csv("../output/bio/background_10k.csv", header = TRUE)
janpresall <- read.csv("../output/bio/pres_nomissing.csv", header = TRUE)
janpresaball <- rbind.fill(janaball, janpresall)
janpresaball <- subset(janpresaball, month == 1)
janpresaball <- subset(janpresaball, select = c(occurrence, longitude_meters, latitude_meters, temp_depth, temp_surface, chl_depth, chl_surface, o2_depth, o2_surface, salinity_depth, salinity_surface, ssh_surface, mlp_surface, nao_sample, nao_prev, nao_winter, amo_sample, amo_prev, amo_winter))
names(janpresaball)[names(janpresaball)=="occurrence"] <- "species"
names(janpresaball)[names(janpresaball)=="longitude_meters"] <- "longitude"
names(janpresaball)[names(janpresaball)=="latitude_meters"] <- "latitude"
janpresall <- subset(janpresaball, species == 1)
janpresall$species <- replace(janpresall$species, janpresall$species == "1", "fish")
write.csv(janpresall, "../output/maxentvariableselection/presence.csv", row.names = FALSE)
janaball <- subset(janpresaball, species == 0)
janpresall$species <- replace(janpresall$species, janpresall$species == "0", "bg")
write.csv(janaball, "../output/maxentvariableselection/background.csv", row.names = FALSE)

VariableSelection(maxent="C:/Users/bunny/Downloads/maxent/maxent.jar", outdir=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/output"), gridfolder=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/testgrid"), occurrencelocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/presence.csv"), backgroundlocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/background.csv"), additionalargs="nolinear noquadratic noproduct nothreshold noautofeature", contributionthreshold=5, correlationthreshold=0.9, betamultiplier=seq(0.5, 3, 0.25))
```

with my manually selected variables for jan (temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
```{r}
janaball <- read.csv("../output/bio/background_10k.csv", header = TRUE)
janpresall <- read.csv("../output/bio/pres_nomissing.csv", header = TRUE)
janpresaball_red <- rbind.fill(janaball, janpresall)
janpresaball_red <- subset(janpresaball_red, month == 1)
janpresaball_red <- subset(janpresaball_red, select = c(occurrence, longitude_meters, latitude_meters, temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter))
names(janpresaball_red)[names(janpresaball_red)=="occurrence"] <- "species"
names(janpresaball_red)[names(janpresaball_red)=="longitude_meters"] <- "longitude"
names(janpresaball_red)[names(janpresaball_red)=="latitude_meters"] <- "latitude"
janpresall_red <- subset(janpresaball_red, species == 1)
janpresall_red$species <- replace(janpresall_red$species, janpresall_red$species == "1", "fish")
write.csv(janpresall_red, "../output/maxentvariableselection/presence_red.csv", row.names = FALSE)
janaball_red <- subset(janpresaball_red, species == 0)
janpresall_red$species <- replace(janpresall_red$species, janpresall_red$species == "0", "bg")
write.csv(janaball_red, "../output/maxentvariableselection/background_red.csv", row.names = FALSE)

VariableSelection(maxent="C:/Users/bunny/Downloads/maxent/maxent.jar", outdir=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/output"), gridfolder=("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/testgrid"), occurrencelocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/presence_red.csv"), backgroundlocations= ("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxentvariableselection/background_red.csv"), additionalargs="nolinear noquadratic noproduct nothreshold noautofeature", contributionthreshold=5, correlationthreshold=0.9, betamultiplier=seq(0.25, 3, 0.25))
```

so this is all lovely... the two runs suggest b-multipliers of <1 (0.75 and 0.25 respectively). In my test runs above, 0.25 gives a 'tighter fit' thatn 1 (the default). Apparently changin the b-multiplier helps reduce over and underfitting... "the default setting in Maxent is 1. Smaller values will constrain the model more, whereas larger numbers will relax the model, making it “smoother”......

maybe try enmval?
